\begin{itemize}
		\item \textbf{[\hypertarget{C1}{C1}]} Logging in whitout being signed up is prevented. 
		\item \textbf{[\hypertarget{C2}{C2}]} Logging in, being already logged in, is impossible. 
		\item \textbf{[\hypertarget{C3}{C3}]} Signing up, being already signed up, is impossible.
		\item \textbf{[\hypertarget{C4}{C4}]} Creating a meeting with the same schedule of an existent one is not allowed. 
		\item \textbf{[\hypertarget{C5}{C5}]} Scheduling a meeting during break pauses, setted in preferences, is prevented. 
		\item \textbf{[\hypertarget{C6}{C6}]} it is impossible to generate an appointment in the past or in an invalid date. 
		\item \textbf{[\hypertarget{C7}{C7}]} Meeting creation requires name,date,hour,location and a starting point to be defined properly.
		\item \textbf{[\hypertarget{C8}{C8}]} At least one mean of travel must be selected.
		\item \textbf{[\hypertarget{C9}{C9}]} Every lunch break must last at least 30 minutes.
		\item \textbf{[\hypertarget{C10}{C10}} If rain or snow are in the forecast, travel by bus is preferred. 
		\item \textbf{[\hypertarget{C11}{C11}]} In case of strikes, routes involving the related travel mean are not considered. 
		\item \textbf{[\hypertarget{C12}{C12}]} Reminders must be setted before the scheduled time of the related events.
		\item \textbf{[\hypertarget{C13}{C13}]} At least one travel mean must be activated in preferences.
		\item \textbf{[\hypertarget{C14}{C14}]} To use the 'Delay notification function' the user have to insert the email of people involved in the meeting.
	\end{itemize}
