This document is structured in seven sections, here is an overview of the contents of each and every one:
\begin{itemize}
	\item \textbf{Introduction}: 
This section provides a general introduction and overview of the Design Document and the covered topics that were not previously taken into account by the RASD. 
	\item \textbf{Architectural Design}:
	This section shows the main system components together with sub-components and their relationship. 
	This section is divided into different parts whose focus is mainly on design choices, interactions, used architectural styles and patterns.  
	\item \textbf{Algorithm Design}: 
This section provides a high-level description and details about some of the most crucial and critical algorithms to be implemented in the system-to-be. 
	\item \textbf{User Interface Design}: 
 It provides an overview on how the user interface will look like and behave giving a more complete view with respect to those contained in the RASD. 
	\item \textbf{Requirements traceability}: 
This section describes how the requirements defined in the RASD are mapped and are satisfied by the design elements and components defined in this document. 
	\item \textbf{Implementation, integration and test plan}: 
This section is used to explain the strategies for implementations and testing that will be adopted in the development part of the project.
\item \textbf{Appendix}: 
Here we provide information about the used software and the effort spent to redact this document. 
\end{itemize}